%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

% Single-line heading for projects (title + links on one row, bullet aligns to title)
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Sanskar Singh Bhardwaj}} & Email: \href{mailto:sanskarsinghty1234@gmail.com}{sanskarsinghty1234@gmail.com}\\ & Mobile:~~~+91-7828652790 \\
  \href{https://github.com/sanskar-singh-2403}{GitHub: sanskar-singh-2403} & LinkedIn: \href{https://www.linkedin.com/in/sanskar-singh-bhardwaj-558771227/}{Sanskar Singh Bhardwaj}\\
  \href{https://sanskar-singh-2403.github.io/}{Portfolio: sanskar-singh-2403.github.io} & \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Naya Raipur}{Raipur, India}
      {Bachelor of Technology - Electronics \& Communication Engineering |  \textbf{GPA: 8.71/10}}{2021 - 2025}
      {}
    \resumeSubheading
      {Delhi Public School}{Bhilai, India}
      {Intermediate  |\textbf{ Percentage: 96\% }}{2019 - 2021}
      {}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading{TailoredAI}{Remote}
    {AI Engineer}{Oct 2025 - Present}
    \resumeItemListStart
      \item{Automated a client's end-to-end hiring pipeline with an agent-driven workflow, cutting time-to-hire from 2 weeks to 3 days and saving ~15 recruiter hours per opening.}
      \item{Built a real-time AI voice interview agent using OpenAI Whisper (STT) and TTS models, running 20+ automated interviews at sub-2s latency.}
      \item{Built a candidate-sourcing engine that profiles and ranks 200+ applicants per opening by scoring past work, resumes, and project fit, cutting shortlisting from hours to minutes.}
    \resumeItemListEnd
\vspace{1pt}

\resumeSubheading{Hyperverge}{Remote}
    {SDE}{Jan 2025 - Oct 2025}
    \resumeItemListStart
      \item{Refactored the INDIA-OCR stack with async thread/process pool executors and in-memory OpenCV image handling, cutting ASG instances 20\% and lifting throughput from 2 to 5 RPS.}
      \item{Optimized GPU inference on Triton (dynamic batching, multi-instance GPU execution, ensembles, model warmup), cutting the peak \texttt{g4dn.2xlarge} ASG from 40 to 10 instances (~75\% GPU cost reduction).}
    \resumeItemListEnd
\vspace{1pt}

\resumeSubheading{TestRigor}{Remote}
    {Full Stack Development Intern}{Nov 2023 - April 2024}
    \resumeItemListStart
      \item{Designed a custom Language Server Protocol (LSP) over JSON-RPC to power intelligent code suggestions in the team's IDE, cutting test authoring time by 20\%.}
      \item{Built an executor service to parallelize test execution across 8 backend instances using Java, Docker, and Kubernetes, cutting test execution time by 40\%.}
    \resumeItemListEnd
\vspace{1pt}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}

\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Cortex - GraphRAG AI Assistant} | \href{https://github.com/sanskar-singh-2403/cortex}{Github}}{}
    \resumeItemListStart
      \item{Built an AI assistant with an MCP backbone that ingests code and documents into a Neo4j knowledge graph, answering multi-hop natural-language queries with cited sources via Graph-RAG and Cypher-to-LLM translation.}
      \item{Parses codebases into ASTs to power semantic code search, automated test generation, and documentation. \textit{Tech: TypeScript, Python, Neo4j, OpenAI, MCP, Zod.}}
    \resumeItemListEnd
\vspace{1pt}

  \resumeProjectHeading
    {\textbf{Events App} | \href{https://github.com/sanskar-singh-2403/events_app}{Github} | \href{https://evently-yy.vercel.app/}{Deployed Link}}{}
    \resumeItemListStart
      \item{A full-stack event management web app to create events and buy tickets, with Stripe integration, Clerk-based authentication, and tag-based search. \textit{Tech: Next.js, MongoDB, Tailwind, ShadCn, Clerk, Stripe.}}
    \resumeItemListEnd
\vspace{1pt}

  \resumeProjectHeading
    {\textbf{Text-Summarizer} | \href{https://github.com/sanskar-singh-2403/text_summarizer}{Github}}{}
    \resumeItemListStart
      \item{Built an abstractive text summarizer using Hugging Face's Pegasus model, served over a FastAPI backend for sequence-to-sequence summarization of long documents. \textit{Tech: Python, Hugging Face Transformers, FastAPI.}}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Achievements and Awards}
\resumeSubHeadingListStart
  \item \small{\textbf{Flipkart Grid 5.0 Finalist} - Qualified for the finals, where a total of 1 lakh teams participated.}
  \item \small{\textbf{Competitive Programming} - Ranked Specialist (1480+) on \textbf{\href{https://codeforces.com/profile/Gustavo_gus}{CodeForces}} and 4 Star (1800+) on \textbf{\href{https://www.codechef.com/users/king_ragnar24}{CodeChef}}.}
  \item \small{Solved over 2500+ problems across \textbf{\href{https://leetcode.com/ken_kaneki12/}{LeetCode}}, \textbf{\href{https://auth.geeksforgeeks.org/user/sanskarsinghty1234}{GFG}}, CodeForces, and CodeChef.}
  \item \small{\textbf{Kaggle Specialist} - Achieved a rank under 400 in the Kaggle RL competition \textbf{\href{https://www.kaggle.com/ghoulreaper}{ghoulreaper}}.}
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills and Technologies}
\vspace{2pt}
{\small C++, Java, Python, JavaScript, TypeScript, Golang, Node.js, Express, React, Next.js, MongoDB, PostgreSQL, Neo4j, Docker, Kubernetes, AWS, Kafka, TensorFlow, OpenAI, LangChain.}
\vspace{-5pt}

\end{document}
